Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

Property-property salinity plot using:

lm2 <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
                     "; P =", signif(lm2$fit$P.param, 3),
                     "; RMSE = ", signif(lm2$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
        datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )
lm2 <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
                     "; P =", signif(lm2$fit$P.param, 3),
                     "; RMSE = ", signif(lm2$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}

fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)

p<-  ggplot(d_all,aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")  +theme_bw()
print(p)

>>>>

```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
  geom_point( aes(color=factor(month))) + 
  geom_abline(slope=1, intercept=0, linetype = "dashed")+
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
  coord_fixed(ratio = 1 )+
  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()

@@

```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# Remove temp_fb outliers 
d_all <- d_all %>%
  dplyr::mutate(
    temp_fb = ifelse(
      datetime >= as.POSIXct("2017-03-22 08:00:00") &
        datetime <= as.POSIXct("2017-03-23 16:00:00"),
      NA,
      temp_fb
    ),
    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
  )
lm <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)

p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs(x="T 11 m", y="T FB ", color = "Months") 
print(p) # p_temp_11_fb

@@

```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
print(p)
